Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme

### 2013-06-18 Report/article.tex
j
ci

\subsection{Cost of the Cryptosystem}
 In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time. These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem. The measurements in this section were taken on M2. From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$. Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation.

@@

\autoref{tab:tradeofftab1} presents the security-cost trade-off for 10000 multiplications as a function of $\eta$. We remark that : decreasing $\eta$ with other parameters fixed increases the security of the system at the cost of decreasing the depth. This confirms equation (1) and (2).  We further note that increasing the value of $\eta$ increases the computational cost as $p$ increases which makes the the ciphertexts longer. On the contrary, \autoref{tab:tradeofftab2} presents the security-cost tradeoff for 10000 multiplications as a function of $\mu$. In this case, increasing $\mu$ with other parameters fixed increases the security of the system(confirms (1)) at the cost of decreasing the depth. With small values of $\mu$, the cost remains stable. However, for larger values, the cost increases considerably and this is due to the fact that, the coefficients of the random polynomial in \texttt{Encrypt} increase  which is reflected in the size of the ciphertexts. Hence it is profitable to increase $\mu$ to increase the security of the system when $\mu$ is not too large

.
\begin{table}[htb]
  \centering
  \caption{Trade-off for 10000 multiplications}
\begin{tabular}{|c|c|c|c||}
  \hline
  \multicolumn{4}{|c||}{$\mu = 4$ , $N=8$} \\
  \hline
  $\eta$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
  \hline
  $2^{600}$ & 619  & 6.90 & 1.009 \\
  $2^{400}$ &  580 & 6.31 & 1.014 \\
  $2^{200}$ &  509 & 5.03 & 1.028 \\
  $2^{100}$ &  490 & 4.28 & 1.059 \\
   \hline
\end{tabular}
\normalsize
\label{tab:tradeofftab1}
\end{table}

\begin{table}[htb]
  \centering
  \caption{Trade-off for 10000 multiplications}
\begin{tabular}{|c|c|c|c||}
  \hline
  \multicolumn{4}{|c||}{$\eta = 2^{300}$ , $N=8$} \\
  \hline
  $\mu$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
  \hline
  $2$ & 527  & 6.90 & 1.01887 \\
  $4$ & 526 & 5.89 & 1.01894 \\
  $8$ & 528  & 5.63 & 1.01900 \\
  $16$ & 529  & 5.40 & 1.01907 \\
  $32$ & 801  & 5.40 & 1.01913 \\
  $64$ & 824  & 5.40 & 1.01920 \\

>>>>

\subsection{Cost of the Cryptosystem}
 In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time. These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem. The measurements in this section were taken on M2. From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$. Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation. The same thing happend to \texttt{Encrypt} which evaluate a polynomial of bigger degree. And as for the rest of function they depend on the size of ciphertext which become bigger because $p$ become bigger.

@@

\autoref{tab:tradeofftab1} presents the security-cost trade-off for 10000 multiplications as a function of $\eta$. We remark that : decreasing $\eta$ with other parameters fixed increases the security of the system at the cost of decreasing the depth. This confirms equation (1) and (2).  We further note that increasing the value of $\eta$ increases the computational cost as $p$ increases which makes the the ciphertexts longer. On the contrary, \autoref{tab:tradeofftab2} presents the security-cost tradeoff for 10000 multiplications as a function of $\mu$. In this case, increasing $\mu$ with other parameters fixed increases the security of the system(confirms (1)) at the cost of decreasing the depth. With small values of $\mu$, the cost remains stable. However, for larger values, the cost increases considerably and this is due to the fact that, the coefficients of the random polynomial in \texttt{Encrypt} increase  which is reflected in the size of the ciphertexts. Hence it is profitable to increase $\mu$ to increase the security of the system when $\mu$ is not too large.

\begin{table}[htb]
  \centering
  \caption{Trade-off for 10000 multiplications}
\begin{tabular}{|c|c|c|c||}
  \hline
  \multicolumn{4}{|c||}{$\mu = 4$ , $N=8$} \\
  \hline
  $\eta$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
  \hline
  $2^{600}$ & 619  & 6.90 & 1.009 \\
  $2^{400}$ &  580 & 6.31 & 1.014 \\
  $2^{200}$ &  509 & 5.03 & 1.028 \\
  $2^{100}$ &  490 & 4.28 & 1.059 \\
   \hline
\end{tabular}
\normalsize
\label{tab:tradeofftab1}
\end{table}

\begin{table}[htb]
  \centering
  \caption{Trade-off for 10000 multiplications}
\begin{tabular}{|c|c|c|c||}
  \hline
  \multicolumn{4}{|c||}{$\eta = 2^{300}$ , $N=8$} \\
  \hline
  $\mu$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
  \hline
  $2$ & 527  & 6.90 & 1.01887 \\
  $4$ & 526 & 5.89 & 1.01894 \\
  $8$ & 528  & 5.63 & 1.01900 \\
  $16$ & 529  & 5.40 & 1.01907 \\
  $32$ & 801  & 5.21 & 1.01913 \\
  $64$ & 824  & 5.04 & 1.01920 \\
